Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-02 paper.tex
extended description
about discretization
Added Bagging subsection

\begin{itemize}
\item \textbf{Bagging}
\item \textbf{Boosting}
\item \textbf{Random Forest}
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman
\cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}

@@

The output variable which is the total sales is a categorical variable the represent the level of the quantity sold of a given book. Four categories are used to represent the total sales level: Low (L), Medium (M), High (H) and Very High (VH). Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in.
% Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined. \\

>>>>

\begin{itemize}
\item \textbf{Bagging} Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced by \citet{B1996}. Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset. The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset. The final classifier's output is based on aggregating the classifiers by taking a majority or weighted vote.

\item \textbf{Boosting}
\item \textbf{Random Forest}
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}

@@

The output variable which is the total sales is a categorical variable the represent the level of the quantity sold of a given book. Four categories are used to represent the total sales level: Low (L), Medium (M), High (H) and Very High (VH). Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in. Discretization of the volume of sales was conducted with the aid of experts in the domain of editorial management business by defining the the four categories.

% Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D
% Hossam - I have added this to the latter paragraph. Please check.

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined for each class. \\
